Quadrotor landing on a moving platform

### 2016-04-05 assignments/presentation/presentation.tex
fixed hyperlinks

\href{https://www.youtube.com/watch?v=9oUxANr1j0o}{Partial Success} \\
and of course a few fails along the way \\
\href{https://youtu.be/2i0S6vrP9oc?t=53}{fails}

@@

\begin{frame}
And here are some of the not so great moments we have had
\begin{itemize}
\item Early attempts at getting the quad to just take off: 
	\begin{itemize}
		\item \hyperlink{https://youtu.be/a6_0YQt9BuM?t=29}{\beamergotobutton{test}} \\
		\item \hyperlink{https://youtu.be/9zpM9thEneg?t=10}{\beamergotobutton{}} \\
		\item \hyperlink{https://youtu.be/5U7R6-7MHrY?t=137}{\beamergotobutton{}}
	\end{itemize}
\item MOCAP dropping out and causing the quad to crash:
		\item \hyperlink{https://youtu.be/ZHCqoEdYbX0?t=30}{\beamergotobutton{crash}}

\item And here is how we tested to see if our commands made sense:
\href{https://youtu.be/0EvrlYkYMyY?t=175}{command checking}

>>>>

\href{https://www.youtube.com/watch?v=9oUxANr1j0o}{\beamergotobutton{Partial Success}} \\
and of course a few fails along the way \\
\href{https://youtu.be/2i0S6vrP9oc?t=53}{\beamergotobutton{Not quite there yet}}

@@

\begin{frame}
And here are some of the not so great moments we have had
\begin{itemize}
\item Early attempts at getting the quad to just take off: 
	\begin{itemize}
		\item \href{https://youtu.be/a6_0YQt9BuM?t=29}{\beamergotobutton{2nd test flight}} \\
		\item \href{https://youtu.be/9zpM9thEneg?t=10}{\beamergotobutton{4th test flight}} \\
		\item \href{https://youtu.be/5U7R6-7MHrY?t=137}{\beamergotobutton{9th test flight}}
	\end{itemize}
\item MOCAP dropping out and causing the quad to crash:
		\item \href{https://youtu.be/ZHCqoEdYbX0?t=30}{\beamergotobutton{crash}}

\item And here is how we tested to see if our commands made sense:
\href{https://youtu.be/0EvrlYkYMyY?t=175}{\beamergotobutton{checking Odroid command inputs}}
